Draft: Bounds on Coding Theory\\from Algebraic Geometry

### 2021-04-10 draft.tex
Final draft

\documentclass[11pt]{amsart}
\usepackage[letterpaper,left=125pt,right=125pt]{geometry}

\usepackage[english]{babel}
\usepackage{amsmath, amssymb, amsfonts, amsthm, graphicx}

@@

\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{alg}[thm]{Algorithm}

\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\newtheorem{conj}[thm]{Conjecture}

\theoremstyle{example}
\newtheorem{prob}[thm]{Problem}
\newtheorem{que}[thm]{Question}

\theoremstyle{remark}
\newtheorem{exmp}[thm]{Example}
\newtheorem{rem}[thm]{Remark}
\newtheorem{claim}[thm]{Claim}  
\renewcommand{\theclaim}{}

@@

\title[Codes from Algebraic Geometry]{Bounds on Coding Theory from Algebraic Geometry}
\author{Guilherme Zeus Dantas e Moura}
\date{last compiled \today} % <---- Change this date to the format YYYY-MM-DD

@@

%\begin{abstract} % NOT REQUIRED
%    Coding theory is concerned with finding efficient ways to encode a message so that one may correct errors in the message. In algebraic coding theory, we study efficient codes generated from algebraic geometric methods.
%    
%    In this paper, I will construct the Reed--Solomon codes, generalize them using projective curves, and understand the results from \cite{TVZ82} on finding a bound better than the well-known Gilbert--Varshamov one.
%\end{abstract}

@@

WRITE INTRODUCTION WITH ALICE AND BOB.

\begin{defn}[Code]
    A \emph{code $C$ over an alphabet $A$} is a subset of $A^n = A \times \cdots \times A$.
    We define $n$ as the \emph{length of $C$}.
    A code $C$ over a field $A$ is a \emph{linear code} if $C$ is a vector subspace of $A^n$. An element of a code $C$ is called a \emph{code word}.
\end{defn}

In this paper, $A$ is a finite field unless otherwise stated.

\begin{defn}[Hamming distance]
    We define \emph{Hamming distance} between $\mathbf{x} = (x_1, \dots, x_n), \mathbf{y} = (y_1, \dots, y_n) \in A^n$ as
    \begin{equation}
		\dist(\mathbf{x}, \mathbf{y}) = \#\left( x_i \neq y_i \mid i \in \{1, 2, \dots, n\} \right),
	\end{equation}
    in other words, the number of positions $\mathbf{x}$ and $\mathbf{y}$ differ.
\end{defn}

\begin{prop}
    Hamming distance is a metric over $A^n$, i.e., the following holds for any $\mathbf{x}, \mathbf{y}, \mathbf{z} \in A^n$:
    \begin{itemize}[noitemsep]
        \item $\dist(\mathbf{x}, \mathbf{y}) = 0 \iff \mathbf{x} = \mathbf{y}$;
        \item $\dist(\mathbf{x}, \mathbf{y}) = \dist(\mathbf{x}, \mathbf{y})$;
        \item $\dist(\mathbf{x}, \mathbf{y}) \le \dist(\mathbf{x}, \mathbf{z}) + \dist(\mathbf{z}, \mathbf{y})$.
    \end{itemize}
\end{prop}

@@

Suppose Alice wants to send a message to Bob through a noisy channel. They previously agree on a choice of code $C \subset A^n$, with parameters $n, k, d$. Alice will choose one of the $|A|^k$ code words and send it to Bob. Since the channel is not a perfect medium, some positions of the code may change; however, if less than $\frac{d}{2}$ of such changes occur, Bob can take the closest code word to the receiving message using Hamming distance and restore the original message.

@@

\begin{defn}
    If $C$ is a code, its code rate is $R = k/n$ and its relative minimum distance is $\delta = d/n$. Note that $R, \delta \in [0, 1]$.
\end{defn}

@@

\begin{proof}
	We will provide the proof for Theorem \ref{thm:singleton_bound} when $C$ is a linear code.

	WRITE PROOF.
\end{proof}

\begin{defn}[Reed--Solomon Codes]\label{defn:rs_codes}
	Let $q$ be a power of a prime, and $\mathbb{F}_q = \{\alpha_1, \alpha_2, \dots, \alpha_q\}$ the field with $q$ elements. Let $k$ be an integer, and ${L}_k$ the set of all polynomials over $\mathbb{F}_q$ with degree smaller than $k$. Let $k \le n \le q$ be an integer. The Reed--Solomon code $RS_q(n, k)$ over $\mathbb{F}_q$ is 
	\begin{equation}
		RS_q(n, k) = \left\{\left(f(\alpha_1), f(\alpha_2), \dots, f(\alpha_n)\right) \mid f \in {L}_k\right\}.
	\end{equation}
\end{defn}

\begin{prop}
	The Reed--Solomon code $R_q(n, k)$ is a linear code with length $n$, dimension $k$ and minimum distance $n - k + 1$.
	Thus, any Reed--Solomon code meets the inequality of the Singleton Bound.
\end{prop}

\begin{proof}
	$R_q(n, k)$ is a subset of $\mathbb{F}_q^n$, thus it has length $n$.  
	Note that $ L_k$ is a vector space over $\mathbb{F}_q$. Note that $\{1, x, x^2, \dots, x^{k-1}\}$ is a choice of basis for this vector space, thus it has dimension $k$. Consider the map $\phi:  L_k \to \mathbb{F}_q^n$ given by 
	\begin{equation}
		f \mapsto (f(\alpha_1), f(\alpha_2), \dots, f(\alpha_n)).
	\end{equation}

@@

The Reed--Solomon codes are very good codes in the sense that key have the largest possible sum $k + d$ for their length $n$. However, Reed--Solomon codes are limited because their length is at most the alphabet size. So, a question naturally arises: Given fixed $\mathbb{F}_q$, are there codes over $\mathbb{F}_q$ with arbitrarily large $n$ and $R + \delta = 1 + 1/n$? If not, how large can $R$ and $\delta$ be when $n$ gets larger? The Gilbert--Varshamov bound shows that there are codes with 
\begin{equation}
	1 - R \approx q(\delta), \text{as $n \to \infty$,}
\end{equation}
in which
\begin{equation}
	q(x) = x \log_q(q-1) - x\log_q(x) - (1-x)\log_q(x).
\end{equation}
Are there any better codes?

\section{Rational Functions and Divisors}

\begin{defn}[Rational Function]
	A rational function $f$	is a function which is the ratio $g/h$ of two polynomials.
	It is homogeneous if $g, h$ are homogeneous.
	After cancelling common roots of $g, h$, the roots of $g$ are called \emph{zeros} of $f$ and the roots of $h$ are called the \emph{poles} of $f$.
\end{defn}

	We say $f$ has order $n$ in $P$ if $P$ is a zero of muliplicity $n$; order $-n$ if $P$ is a pole with multiplicity $n$; order $0$, otherwise.

\begin{defn}[Divisor] 
	Let $F$ be the algebraic closure of $\mathbb{F}_q$.
	Let $X$ be an irreducible nonsingular projective curve in $N$-dimensional projective space over $F$.
	A \emph{divisor} on $X$ is a formal finite sum of the form $D = \sum a_P P$, where $P$ are points of $X$, $a_P$ are integers and $a_P = 0$ for all but finitely many points $P$.
	The \emph{degree} of $D$ is $\sum n_P$.
	The \emph{support} $\Supp D$ is the set $\{P \in X : a_P \neq 0\}$
\end{defn}

If $D = \sum n_p P$, then define the vector space $\mathcal L(D)$ as the set of all homogeneous rational functions $f$ such that the order of $f$ at each point $P$ of $X$ is greater or equal to $n_P$.
For our study, an important theorem is the following:
\begin{thm}[Riemman--Roch Theorem, \cite{Wal00}]
	Let $X$ be a nonsingular projective curve of genus\footnote{For the reader that is not familiar with genus, it is enough to know that it is an integer that can be calculated for any given curve.} $g$ defined over the field $\mathbb{F}_q$ and let $D$ be a divisor on $X$. Then
	\begin{equation}
		\dim \mathcal L(D) \ge \deg D + 1 - g,
	\end{equation}
	with equality holding if $\deg D > 2g - 2$.
\end{thm}

%Note that, if the degree of $D$ is negative, then
%\begin{equation}
%	\mathcal L(D) = \{0\}.
%\end{equation}
%Additionally, the \emph{Riemann--Rock theorem} implies that the dimension of the vector space $\mathcal L(D)$ is 
%\begin{equation}
%	 \dim\mathcal L(D) \ge \deg D - g + 1,
%\end{equation}
%where $g$ denotes the genus of $X$ (for the reader who is not familiar with the term genus, it suffices to know that it is an integer which can be calculated for any given curve).

\section{Generalized Reed--Solomon codes} \label{s:grs}
Let $\mathbb{P}^1(\mathbb{F}_q)$ denote the projective line over $\mathbb{F}$. We will write $(a : b)$ to denote the projective point corresponding to the $1$-dimensional vector space through $(a, b)$. The points on $\mathbb{P}^1(\mathbb{F}_q)$ are the points
\begin{equation}
	P_i = (\alpha_i : 1), \qquad 1 \le i \le q,
\end{equation}
and
\begin{equation}
	P_\infty = (1 : 0).
\end{equation}

Following \cite{LS87}, let $\mathcal L_k$ be the set of two-variable homogeneous rational functions which have a pole of order less than $k$ in the point $Q$.

\begin{prop}
	The sets $\mathcal L_k$ and $L_k$ are mapped with a bijection $\phi: f(x) \mapsto f(x/y)$.
\end{prop}
\begin{proof}
	WRITE PROOF.
\end{proof}

Then, we can rewrite the Reed--Solomon code from \ref{defn:rs_codes} as
\begin{equation}
	RS_q(n, k) = \{f(P_1), f(P_2), \dots, f(P_n) \mid f \in \mathcal L_k\}.
\end{equation}

\begin{defn}[Algebraic Geometric Code]
\end{defn}

We want large $R$ and $\delta$, and these codes yield 
	\begin{equation}
		\label{eq:g/n} R + \delta \ge 1 + 1/n - g/n,
	\end{equation}
where $n$ is the number of rational points of a curve $X$, with genus $g$.

\section{Final thoughts} \label{s:tvz} On equation \eqref{eq:g/n}, we observe that good algebraic geometric codes are generated by curves with a large ratio between $n$ and $g$. On \cite{TVZ82}, the authors present a sequence of such curves, with $n/g$ large enough to create a better bound than the Gilbert--Varshamov one.

>>>>

\documentclass[11pt, oneside]{amsart}
\usepackage[letterpaper,left=125pt,right=125pt]{geometry}

\usepackage[english]{babel}
\usepackage{amsmath, amssymb, amsfonts, amsthm, graphicx}
\usepackage[mathscr]{eucal}

@@

\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{prop}[thm]{Proposition}

\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}

\theoremstyle{remark}
\newtheorem{rem}[thm]{Remark}

@@

\usepackage{todonotes}
\setuptodonotes{size=\tiny, linecolor=black, backgroundcolor=yellow!30}

\usepackage{makecell}

\title[Draft: Codes from Algebraic Geometry]{Draft: Bounds on Coding Theory\\from Algebraic Geometry}
\author{Guilherme Zeus Dantas e Moura}
\date{2021-04-09} % <---- Change this date to the format YYYY-MM-DD

@@

%\begin{abstract} % NOT REQUIRED
%	Coding theory is concerned with finding efficient ways to encode a message so that one may correct errors in the message.
%	In algebraic coding theory, we study efficient codes generated from algebraic geometric methods.
%    
%    In this paper, I will construct the Reed--Solomon codes, generalize them using projective curves, and understand the results from \cite{TVZ82} on finding a bound better than the well-known Gilbert--Varshamov one.
%\end{abstract}

@@

Suppose Alice wants to send a message to Bob though a noisy channel.
When Bob receives the message, it is possible that some of the information is misinterpreted.
For example, if Alice sends the message `\texttt{food}' through the noisy channel, one of its letters may be misinterpreted and Bob could actually receive `\texttt{\underline{m}ood}'.
So, the question Coding Theory tries to answer is:
How can Alice and Bob agree on a system beforehand so that, if Alice sends a message to Bob, even if some misinterpretations occur, Bob will be able to understand the correct meaning?

\begin{defn}[Code] \label{defn:code}
    A \emph{code $C$ over an alphabet $A$} is a subset of $A^n = A \times \cdots \times A$.
    We define $n$ as the \emph{length of $C$}.
	An element of a code $C$ is called a \emph{code word}.
	A code $C$ over a finite field $\mathbb{F}_q$ is a \emph{linear code} if $C$ is a vector subspace of $\mathbb{F}_q^n$.
\end{defn}

Back to the analogy with Alice and Bob, the code $C$ is the set of all the messages that Alice may send to Bob, according to their agreement.

\begin{defn}[Hamming distance] \label{defn:hamming}
    We define \emph{Hamming distance} between $\mathbf{x} = (x_1, \dots, x_n), \mathbf{y} = (y_1, \dots, y_n) \in A^n$ as
    \begin{equation}
		\dist(\mathbf{x}, \mathbf{y}) = \#\left(i \in \{1, 2, \dots, n\} \mid x_i \neq y_i\right),
	\end{equation}
    in other words, the number of positions $\mathbf{x}$ and $\mathbf{y}$ differ.
\end{defn}

\begin{prop} \label{prop:hamming}
    Hamming distance is a metric over $A^n$, i.e., the following holds for any $\mathbf{x}, \mathbf{y}, \mathbf{z} \in A^n$:
    \begin{itemize}[noitemsep]
        \item $\dist(\mathbf{x}, \mathbf{y}) = 0 \iff \mathbf{x} = \mathbf{y}$;
        \item $\dist(\mathbf{x}, \mathbf{y}) = \dist(\mathbf{x}, \mathbf{y})$;
        \item $\dist(\mathbf{x}, \mathbf{y}) \le \dist(\mathbf{x}, \mathbf{z}) + \dist(\mathbf{z}, \mathbf{y})$.
    \end{itemize}
\end{prop}

@@

Alice and Bob agree on a choice of code $C \subset A^n$, with parameters $n, k, d$.
To send a message, Alice will choose one of the $|A|^k$ code words and send it to Bob.
Since the channel is not a perfect medium, some positions of the code may change;
however, if less than $\frac{d}{2}$ of such changes occur, Bob can take the closest code word to the receiving message using Hamming distance and restore the original message.

@@

\begin{defn}
	If $C$ is a code, its \emph{code rate} is $R = k/n$ and its \emph{relative minimum distance} is $\delta = d/n$.
	Note that $R, \delta \in [0, 1]$.
\end{defn}

@@

\begin{proof}
	We will provide the proof for Theorem \ref{thm:singleton_bound} when $C$ is a linear code.\todo{Write proof}
\end{proof}

\begin{defn}[Reed--Solomon codes, \cite{LS87}]\label{defn:rs_codes}
	Let $q$ be a power of a prime, and $\mathbb{F}_q = \{\alpha_1, \alpha_2, \dots, \alpha_q\}$ the field with $q$ elements.
	Let $k$ be an integer, and ${L}_k$ the set of all polynomials over $\mathbb{F}_q$ with degree smaller than $k$.
	Let $k \le n \le q$ be an integer. The Reed--Solomon code $RS_q(n, k)$ over $\mathbb{F}_q$ is 
	\begin{equation}
		RS_q(n, k) = \left\{\left(f(\alpha_1), f(\alpha_2), \dots, f(\alpha_n)\right) \mid f \in {L}_k\right\}.
	\end{equation}
\end{defn}

\begin{prop}
	The Reed--Solomon code $RS_q(n, k)$ is a linear code with length $n$, dimension $k$ and minimum distance $n - k + 1$.
	Thus, any Reed--Solomon code meets the inequality of the Singleton Bound.
\end{prop}

\begin{proof}
	$RS_q(n, k)$ is a subset of $\mathbb{F}_q^n$, thus it has length $n$.  
	Note that $ L_k$ is a vector space over $\mathbb{F}_q$.
	Note that $\{1, x, x^2, \dots, x^{k-1}\}$ is a choice of basis for this vector space, thus it has dimension $k$.
	Consider the map $\phi:  L_k \to \mathbb{F}_q^n$ given by 
	\begin{equation}
		f \mapsto (f(\alpha_1), f(\alpha_2), \dots, f(\alpha_n)).
	\end{equation}

@@

The Reed--Solomon codes are very good codes in the sense that key have the largest possible sum $k + d$ for their length $n$.
However, Reed--Solomon codes are limited because their length is at most the alphabet size.
So, a question naturally arises: Given fixed $\mathbb{F}_q$, are there codes over $\mathbb{F}_q$ with arbitrarily large $n$ and $R + \delta = 1 + 1/n$?
If not, how large can $R$ and $\delta$ be when $n$ gets larger?
The well-known Gilbert--Varshamov bound shows that there are codes with 
\begin{equation}
	1 - R \approx H_q(\delta), \text{ as $n \to \infty$,}
\end{equation}
in which
\begin{equation}
	H_q(x) = x \log_q(q-1) - x\log_q(x) - (1-x)\log_q(x).
\end{equation}
The article \cite{TVZ82} uses Algebraic Geometry to show that there are codes that give better bounds.

\section{Curves, Rational Functions and Divisors}

Through this section, let $K$ be a field and $L$ its algebraic closure.

\begin{defn}[Algebraic curves]
	An affine algebraic plane curve $\mathfrak C_f$ is the zero set of a polynomial $f \in K[x, y]$.
	A projective algebraic plane curve $\mathfrak C_F$ is the zero set in a projective plane of a homogeneous polynomial $F \in K[X, Y, Z]$.
	Generally, algebraic curves are algebraic varieties of dimension $1$.
\end{defn}

Note that there exists a bijection, called \emph{homogenization}, between the polynomials in $K[x, y]$ and the homogeneous polynomials in $K[X, Y, Z]$ defined by $f(x, y) \mapsto Z^{\deg f}f(X/Z, Y/Z)$.
Because of this, we'll denote by $\mathfrak C$ both $\mathfrak C_f$ and $\mathfrak C_F$, where the usage is clear by context.

\begin{defn}[Rational points, \cite{Wal00}] %Not word-by-word
	Let $\mathfrak C$ be a projective curve defined by $F(X, Y, Z) = 0$, where $F \in K[X, Y, Z]$ is homogeneous polynomial.
	A point $(X_0 : Y_0 : Z_0) \in \mathbb{P}^2(L)$ is called a \emph{$L$-rational point} on $\mathfrak C$ if $F(X_0, Y_0, Z_0) = 0$.
	Additionally, if $(X_0 : Y_0 : Z_0)$ is also in $\mathbb{P}^2(K)$, we call it simply a \emph{rational point} on $\mathfrak C$.
\end{defn}

\begin{thm}[Bezout's theorem, \cite{Wal00}] %Not word-by-word
	If $F, G \in K[X, Y, Z]$ are homogeneous polynomials of degrees $d$ and $e$, respectively, then their curves $\mathfrak C_F$ and $\mathfrak C_G$ intersect in exactly $de$ $L$-rational points, counting multiplicity.
\end{thm}

\begin{defn}[Rational function]
	A rational function $f$ over a $K$ is the ratio $g/h$ of polynomials $g, h \in K[x, y]$.
	A homogeneous rational function $F$ over a $K$ is the ratio $G/H$ of homogeneous polynomials $G, H \in K[x, y]$.

	After cancelling common roots of $g, h$, the roots of $g$ are called \emph{zeros} of $f$ and the roots of $h$ are called the \emph{poles} of $f$.

	We say $f$ has order $n$ in $P$ if $P$ is a zero of multiplicity $n$; order $-n$ if $P$ is a pole with multiplicity $n$; and order $0$, otherwise.
\end{defn}

\begin{defn}[Divisor] 
	Let $\overline{\mathbb{F}_q}$ be the algebraic closure of $\mathbb{F}_q$.
	Let $\mathfrak C$ be a projective plane curve defined over $\mathbb{F}_q$.
	A \emph{divisor} $D$ on $\mathfrak C$ is a formal finite sum of the form $D = \sum a_P P$, where $P$ are points of $\mathfrak C$, $a_P$ are integers and $a_P = 0$ for all but finitely many points $P$.
	The \emph{degree} of $D$ is $\sum n_P$.
	The \emph{support} $\Supp D$ is the set $\{P \in X : a_P \neq 0\}$.
\end{defn}

\begin{defn}[Field of rational functions on a curve, \cite{Wal00}] %Copied
	Let $F$ be the polynomial which defines the nonsingular projective plane curve $C$ over the field $\mathbb{F}_q$. The \emph{field of rational functions on $C$} is
	\begin{equation}
		\mathbb{F}_q(C) := \left(\left\{\frac{G}{H}\, \bigg|\,\, \makecell{G, H \in \mathbb{F}_q[X, Y, Z]\\\text{are homogeneous}\\\text{of the same degree}} \right\} \cup \{0\}\right) / \sim
	\end{equation}
	where $g/h \sim g'/h'$ if, and only if, $gh' - g'h \in \langle F \rangle \subset \mathbb{F}_q[X, Y, Z]$.
	\todo{Redefine it in a way that actually shows it is pretty simple.}
\end{defn}

\begin{defn}[\cite{LS87}]
	If $D = \sum n_p P$, then define the vector space $\mathcal L(D)$ as the set of all homogeneous rational functions $f$ such that the order of $f$ at each point $P$ of $\mathfrak C$ is greater or equal to $-n_P$.
\end{defn}

For our study, an important theorem is the following:
\begin{thm}[Riemman--Roch Theorem, \cite{Wal00}]
	Let $\mathfrak C$ be a nonsingular projective curve of genus%
	\footnote{For the reader that is not familiar with genus, it is enough to know that it is an integer that can be calculated for any given curve.}
	$g$ defined over the field $\mathbb{F}_q$ and let $D$ be a divisor on $\mathfrak C$.
	Then
	\begin{equation}
		\dim \mathcal L(D) \ge \deg D + 1 - g,
	\end{equation}
	with equality holding if $\deg D > 2g - 2$.
\end{thm}

%Note that, if the degree of $D$ is negative, then
%\begin{equation}
%	\mathcal L(D) = \{0\}.
%\end{equation}
%Additionally, the \emph{Riemann--Rock theorem} implies that the dimension of the vector space $\mathcal L(D)$ is 
%\begin{equation}
%	 \dim\mathcal L(D) \ge \deg D - g + 1,
%\end{equation}
%where $g$ denotes the genus of $\mathfrak C$ (for the reader who is not familiar with the term genus, it suffices to know that it is an integer which can be calculated for any given curve).

\section{Generalized Reed--Solomon codes} \label{s:grs}
Let $\mathbb{P}^1(\mathbb{F}_q)$ denote the projective line over $\mathbb{F}_q$.
We will write $(a : b)$ to denote the projective point corresponding to the $1$-dimensional vector space through $(a, b)$.
The points on $\mathbb{P}^1(\mathbb{F}_q)$ are the points
\begin{equation}
	P_i = (\alpha_i : 1), \quad 1 \le i \le q, \qquad \text{and} \qquad 
	P_\infty = (1 : 0).
\end{equation}

Consider the divisor $D = (k-1)P_\infty$ and the associated vector space $\mathcal L(D)$, which can be seen as the set of two-variable homogeneous rational functions which have a pole of order less than $k$ in the point $P_\infty$.

\begin{prop}
	The sets $L_k$ and $\mathcal L(D)$ are mapped with a bijection (homogenization) $\phi: f(x) \mapsto Y^{\deg f} f(X/Y)$.
\end{prop}
\begin{proof}
	\todo{Write proof.}
\end{proof}

Then, we can rewrite the Reed--Solomon code from Definition \ref{defn:rs_codes} as
\begin{equation}
	RS_q(n, k) = \{f(P_1), f(P_2), \dots, f(P_n) \mid f \in \mathcal L(D)\}.
\end{equation}

Here, we are evaluating the function $f$ in the points of the projective line.
We shall generalize the idea by changing the projective line to an arbitrary projective curve, and allowing other divisors $D$.

\begin{defn}[Algebraic geometric codes, \cite{LS87, Wal00}] %Copied from Wal00
	Let $\mathfrak C$ be an irreducible nonsingular%
	\todo{Provide an explanation for why the `irreducible nonsingular' is there, but not a thing that the reader should worry. I think the key is some sort of multiplicity.}
	projective plane curve, let $D$ be a divisor on $\mathfrak C$ and let $\mathcal P = \{P_1, P_2, \dots, P_n\}$ be a set of rational points on $\mathfrak C$.
	Assume $\mathcal P$ and $\Supp D$ have no points in common, thus, no $P_i$ can be a pole of any $f \in \mathcal L(D)$, and $f(P_i)$ is well-defined for any $f \in \mathcal L(D)$ and any $P_i \in \mathcal P$.
	Then, the \emph{algebraic geometric code} associated to $\mathfrak C, \mathcal P$ and $D$ is
	\begin{equation}
		C(\mathfrak C, \mathcal P, D) := \{(f(P_1), \dots, f(P_n)) \mid f \in L(D)\} \subset \mathbb{F}_q^n.
	\end{equation}
\end{defn}

\begin{thm}[\cite{Wal00}]
	Let $\mathfrak C, \mathcal P, D$ be as above. Let $g$ denote the genus of $\mathfrak C$. Suppose $D$ satisfies $2g - 2 < \deg D < n$. Then the algebraic geometric code $C(\mathfrak C, \mathcal P, D)$ is linear of:
	\begin{enumerate}[label = \textbullet, itemsep = 0pt]
		\item length $n$,
		\item dimension $\deg D + 1 - g$,
		\item minimum distance $d \ge n - \deg D$.
	\end{enumerate}
\end{thm}

\begin{proof}
	\todo{Write proof.}
\end{proof}

We want large $R$ and $\delta$, and these codes yield 
	\begin{equation}
		\label{eq:g/n} R + \delta \ge 1 + 1/n - g/n,
	\end{equation}
where $n$ is the number of rational points of a curve $\mathfrak C$, with genus $g$; this is an interesting result!
All the work done can be applied for algebraic curves in higher dimensional projective spaces.

\section{Final thoughts}\label{s:tvz}

On equation \eqref{eq:g/n}, we observe that good algebraic geometric codes are generated by curves with a small ratio between $g$ and $n$.
On \cite{TVZ82},\todo{Talk a bit more about it.} the authors present a sequence of such curves, with $g/n$ large enough to create a better bound than the Gilbert--Varshamov one.
